### 2022-07-24 paper/localpsf.tex
more writing in numerical results section

		(optional) Modify $\mathbf{A}_H$ to make $\mathbf{A}_H^{\text{sym}+}$ (Section \ref{sec:make_spd})

@@

>>>>

		(optional) Modify $\mathbf{A}_H$ to make $\mathbf{A}_H^{\text{sym}+}$ (Appendix \ref{sec:make_spd})

@@

In Figure \ref{fig:generalized_eigenvalues} we show the generalized eigenvalues $\lambda$ for the generalized eigenvalue problem
\begin{equation*}
	H u = \lambda P u.
\end{equation*}
Here $H$ is the Hessian evaluated at the reconstructed parameter $\basalfriction$ for $\gamma$ chosen to satisfy the Morozov discrepancy principle. The matrix $P$ is one of the PSF (1), PSF (5), or PSF (25) Gauss-Newton Hessian approximations constructed at that $\basalfriction$, or the regularization Hessian. The PSF preconditioners cluster the eigenvalues of the Hessian near $1$, with more batches yielding better clustering. The regularization preconditioner clusters the trailing eigenvalues but amplifies leading eigenvalues. In Figure \ref{fig:condition_number} we show the condition number of the preconditioned Hessian $P^{-1}H$, and preconditioned Gauss-Newton Hessian, $P^{-1}H_\text{gn}$. The condition numbers are similar for both the Hessian and the Gauss-Newton Hessian. The PSF preconditioners yield the the smallest condition numbers, with more batches yielding smaller condition numbers. Regularization preconditioning and no preconditioning yield larger condition numbers, with regularization preconditioning actually increasing the condition number as compared to no preconditioning.
